Reducing iptables configuration complexity using chains

### 2014-03-27 iptables_newline2014/presentation.tex
add match parameter

      \small{iptables -A INPUT -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -p tcp --dport http -j ACCEPT\\
      iptables -A INPUT -p tcp --dport https -j ACCEPT\\

@@

      \small{iptables -A INPUT -p tcp --dport ssh -s 10.0.0.0/8 -j ACCEPT}

@@

      \small{iptables -A INPUT -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -p tcp --dport https -j ACCEPT\\

@@

      iptables -A INPUT -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -p tcp --dport https -j ACCEPT\\

@@

      iptables -A INPUT -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -p tcp --dport https -j ACCEPT}

@@

      iptables -A INPUT -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -p tcp --dport https -j ACCEPT\\
      iptables -A OUTPUT -p tcp --sport ssh -j ACCEPT\\
      iptables -A OUTPUT -p tcp --sport 80 -j ACCEPT\\
      iptables -A OUTPUT -p tcp --sport https -j ACCEPT}

>>>>

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport http -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -s 10.0.0.0/8 -j ACCEPT}

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\

@@

      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\

@@

      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      iptables -A OUTPUT -m tcp -p tcp --sport ssh -j ACCEPT\\
      iptables -A OUTPUT -m tcp -p tcp --sport 80 -j ACCEPT\\
      iptables -A OUTPUT -m tcp -p tcp --sport https -j ACCEPT}
